\speculake: Hiding Malware in Speculative Execution

### 2018-07-30 paper/architecture.tex
n to m dash

Most notably instructions that use the extended x86 registers are still valid
within the speculative context. Specifically, Intel's hardware accelerated
AES-NI encryption and decryption instructions, which each use 128-bit registers.
As shown in Figure~\ref{fig:spec-capacity}, speculative environments can
complete a significant number of AES rounds -- more than enough to decrypt a
full block using AES-CBC. We investigate the use of AES instructions in the
spculative environment further in Sections~\ref{subsec:decryption}.

>>>>

Most notably instructions that use the extended x86 registers are still valid
within the speculative context. Specifically, Intel's hardware accelerated
AES-NI encryption and decryption instructions, which each use 128-bit registers.
As shown in Figure~\ref{fig:spec-capacity}, speculative environments can
complete a significant number of AES rounds---more than enough to decrypt a
full block using AES-CBC. We investigate the use of AES instructions in the
spculative environment further in Sections~\ref{subsec:decryption}.
